Red Oak: Something Something Algorithmic Policy

### 2015-05-06 draft.tex
removed Ctrl from forwarding_policy, instead representing rules as forwarding_decision option with None interpreted as Ctrl
..

   \subsection*{Forwarding Decision}
   % can give constant decision (e.g. drop() or fwd(loc) to a certain location loc), or decision based on values of the packet (e.g. deliver() which forwards to dst)
   Under the big switch model, the forwarding decisions returned by algorithmic policies are destination-based rather than path-based. For example, the algorithmic policy may decide to deliver a packet, at which point this interpretation will be interpreted as forwarding a packet along a path terminating at the packet's destination. Packets may also be dropped, or forwarding to a static location. Our model also allows for dynamic forwarding based on component of relation, for example to the last seen location of a host according to a MAC-learning controller.

@@

  let filter_src_range
  (f: packet -> forwarding_decision)
  (r:range)
  (pkt: packet) : forwarding_decision =
 if in_range pkt IpSrc r then
    f pkt
 else
   Drop   
\end{lstlisting}

@@

type forwarding_decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of forwarding_decision * forwarding_decision
	| Ctrl

>>>>

   \subsection*{Forwarding Decision}
   % can give constant decision (e.g. drop() or fwd(loc) to a certain location loc), or decision based on values of the packet (e.g. deliver() which forwards to dst)
   Under the big switch model, the forwarding decisions returned by algorithmic policies are destination-based rather than path-based. For example, the algorithmic policy may decide to deliver a packet, at which point this interpretation will be interpreted as forwarding a packet along a path terminating at the packet's destination. Packets may also be dropped, or forwarding to a static location. Our model also allows for dynamic forwarding based on component of relation, for example to the last seen location of a host according to a MAC-learning controller (not shown in Fig~\ref{fig:range_api}).

@@

let filter_src_range f r pkt =
 if in_range pkt IpSrc r then
    f pkt
 else
   Drop   
\end{lstlisting}

@@

type forwarding_decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of forwarding_decision * forwarding_decision
